Topic Scores

### 2019-02-19 test_delete_later_sofia.Rmd

---
title: "Topic Scores"
author: "DARS"
date: "2/18/2019"
output: pdf_document
---
#Set up
##Libraries
```{r libraries}
```
##Raw Data
```{r setup, include=FALSE}
#
##d_course and d_transcript
load("Output/data_pillar_1.RDATA")

@@

##getting top courses per student
```{r topic score student}
student$topic_score <- beta_description$k35%>%
  filter(term %in% student$kw_policy) %>%
  group_by(topic)%>% #maybe we can do this with transcripts afterwards
  summarize(B_score= sum(beta))%>%
  ungroup()%>%
  mutate(Total_b      = sum(B_score),
         B_proportion = B_score/Total_b) %>%
  arrange(desc(B_score))

@@

##Getting courses
```{r course_score}

student$course_score <- gamma_descriptions$k35     %>%
  full_join(student$topic_score, by = "topic") %>%
  mutate(X = gamma * B_proportion)             %>%
  group_by(document)                           %>%
  summarise(course_score = sum(X))             %>%
  arrange(desc(course_score)) %>%
  left_join(
    select(d_course, `Course ID`, `Course Title`),
    by = c("document" = "Course ID")
    )
```
###View
```{r View course}
View(student$topic_score)
View(student$course_score)
```

>>>>

---
title: "Topic Scores"
author: "DARS"
date: "2/18/2019"
output: pdf_document
---
#Set up
##Libraries
```{r libraries}
library(tidyverse)
```
##Raw Data
```{r setup, include=FALSE}
#
##d_course and d_transcript
load("Output/data_pillar_1.RDATA")

@@

##getting top courses per student
```{r topic score student}
standardize <- function (col) {
  col/sum(col)
}

#
##key word Contributions to Topic
 contribution_to_topics <- beta_description$k35                       %>%
  filter(term %in% student$kw_policy)       %>%
  arrange(topic, desc(beta))                %>%
  spread(key=topic, value=beta)             %>%
  mutate_at(.vars = vars(num_range("Topic ",1:35)),
            .funs = standardize)

@@

##Topic contribution to course
```{r course_score}

#
## Topic contribution to course
gamma_descriptions$k35     %>%
  full_join(student$topic_score, by = "topic") %>%
  group_by(document, topic)                           %>%
  summarise(total_gamma= sum(gamma))
  mutate(X = gamma * B_proportion)             %>%
  group_by(document)                           %>%
  summarise(course_score = sum(X))             %>%
  arrange(desc(course_score))                  %>%
  left_join(
    select(d_course, `Course ID`, `Course Title`),
    by = c("document" = "Course ID")
    )

```
###View
```{r View course}
View(student$topic_score)
View(student$course_score)
```
